% --- LaTeX CV Template - S. Venkatraman ---

% Set document class and font size
\documentclass[letterpaper, 12pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}
\renewcommand{\thefootnote}{}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}


% Remove page numbering
% \pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Yuhan Zhang} \hfill{\it\footnotesize} }

% --- Contact information and other items ---

\vspace{0.5cm} 

\begin{tabular}{ll}
\hspace{-0.9cm} Undergraduate & \hspace{3cm} \textbf{Email}: 
begemotnp@gmail.com\\
\hspace{-0.8cm}Major in Automation& \hspace{3cm} \textbf{WeChat}: EriclanZh\\
\hspace{-0.8cm}College of Electrical Engineering                 & \\
\hspace{-0.8cm}Zhejiang University& \end{tabular}



% --- Section: Research interests ---
\subsection*{\color{OliveGreen} Research interests}
My research interest lies in the theories of Online Learning, Bandits and Causal Inference. I am eager to deepen my understanding and contribute to advancements in these areas through study and research. 

% --- Section: Education ---
\subsection*{\color{OliveGreen} Education }

\begin{flushleft}
    \textbf{Zhejiang University, Hangzhou, China }   \\
   B.Eng. in Automation, College of Electrical Engineering  \hfill August 2023 - Present

\textit{Overall GPA}: 4.48/5.0\\
\textit{Expected Graduation}: June 2027 \\

\end{flushleft}

\subsection*{\color{OliveGreen} Research Experience}
\textbf{Learning and INference Systems (LINs) Lab, Westlake University }   \\
\hfill April 2025 – September 2025 \\
        I conducted research under the supervision of Prof. Tao Lin, focusing on discrete diffusion models.
\\\\
\textbf{Independent Research, supervised by Prof. Xin Liu, ShanghaiTech University} \\
\hfill December 2025 – Present \\
I am conducting independent research on online large language model (LLM) routing under the supervision of Prof. Xin Liu. My work focuses on formulating the routing problem as an online learning task and exploring bandit-based approaches for adaptive model selection under partial feedback.

\subsection*{\color{OliveGreen} Projects}

\textbf{LLM-based Study Abroad Application Assistant (RAG System)} \\
\hfill November 2025 \\
Designed and implemented a retrieval-augmented generation (RAG) system for study abroad application assistance. Built a document knowledge base covering university programs, application requirements, and personal statement guidelines. Integrated multi-query fusion retrieval and cross-encoder re-ranking to improve answer precision under long-context queries. 


% --- Section: Awards, scholarships, etc. ---

\subsection*{\color{OliveGreen} Honors and Awards}
\begin{flushleft}
     Third-Class Scholarship, Zhejiang University   \hfill 2024 \\
   Third-Class Scholarship, Zhejiang University   \hfill 2025 \\
    Kinlead Scholarship \hfill 2025 \\
\end{flushleft}


\subsection*{\color{OliveGreen} Skills}
\begin{flushleft}
   {\textbf{Programming Languages:}} Python, C, MATLAB
   
\end{flushleft}
\clearpage














% --- End of CV! ---

\end{document}